SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-07-25 scipy-1.0/subpackages.tex
Add a bit of context to the submodule organization section.

The SciPy library is organized as a collection of subpackages.  Here we
summarize the scope and capabilities of each subpackage.

>>>>

The SciPy library is organized as a collection of subpackages.  The 16
subpackages include mathematical building blocks (e.g. linear algebra, Fourier
transforms, special functions), data structures (e.g. sparse matrices, k-D trees),
algorithms (e.g. numerical optimization and integration, clustering, interpolation,
graph algorithms, computational geometry), and higher-level data analysis
functionality (e.g. signal and image processing, statistical methods).

Here we summarize the scope and capabilities of each subpackage.
